Competing Bandits

### 2018-08-07 paper/competing_bandits.tex
update some figures + some more writing

\begin{table}[ht]
\centering
\caption{Needle In Haystack Prior} 
\begin{tabular}{rlll}
  \hline
Alg 1 vs 2 & k = 20 & k = 100 & k = 200 \\ 
  \hline
TS vs DG & \makecell{\textbf{0.66} $\pm$0.05\\ eeog \\ avg: 330\\ med: 31} & \makecell{\textbf{0.61} $\pm$0.05\\ eeog \\ avg: 590\\ med: 61.5} &  \\
\hline 
  TS vs DEG & \makecell{\textbf{0.58} $\pm$0.06\\ eeog \\ avg: 180\\ med: 1} & \makecell{\textbf{0.54} $\pm$0.05\\ eeog \\ avg: 670\\ med: 60} &  \\ 
  \hline 
  DG vs DEG & \makecell{\textbf{0.41} $\pm$0.05\\ eeog \\ avg: 650\\ med: 182} & \makecell{\textbf{0.41} $\pm$0.05\\ eeog \\ avg: 1500\\ med: 672} &  \\ 
   \hline
   \label{hm_nih}
   \end{tabular}
\caption*{\tiny{The first line in each cell contains the average market share received by the firm playing Alg 1 (and the market share of Alg 2 is 1 - Alg 1 Market Share) as well as a 95 \% confidence band. For example, the cell in the top left indicates that TS gets on average 32\% of the market when played against DG. The next line contain the average and median effective end of game for this set of simulations.}}
\end{table}

\begin{table}[ht]
\centering
\caption{Heavy Tail Prior} 
\begin{tabular}{rlll}
  \hline
Alg 1 vs 2 & k = 20 & k = 100 & k = 200 \\ 
  \hline
TS vs DG & \makecell{\textbf{0.32} $\pm$0.05\\ eeog \\ avg: 150\\ med: 0} & \makecell{\textbf{0.55} $\pm$0.05\\ eeog \\ avg: 300\\ med: 0} & \makecell{\textbf{0.73} $\pm$0.04\\ eeog \\ avg: 1400\\ med: 226.5} \\ 
\hline
  TS vs DEG & \makecell{\textbf{0.34} $\pm$0.05\\ eeog \\ avg: 36\\ med: 0} & \makecell{\textbf{0.65} $\pm$0.05\\ eeog \\ avg: 330\\ med: 0} & \makecell{\textbf{0.91} $\pm$0.02\\ eeog \\ avg: 1100\\ med: 107.5} \\ 
  \hline
  DG vs DEG & \makecell{\textbf{0.62} $\pm$0.05\\ eeog \\ avg: 800\\ med: 10} & \makecell{\textbf{0.6} $\pm$0.05\\ eeog \\ avg: 1500\\ med: 866.5} & \makecell{\textbf{0.62} $\pm$0.05\\ eeog \\ avg: 1900\\ med: 1627.5} \\ 
   \hline
   \label{hm_ht}
\end{tabular}
\end{table}

@@

@@

[Discuss that, under random agent models, firms that play better learning algorithms do better in the long-run since they get enough free agents to move to the part of the relative reputation curve where better algorithms win]

[Discuss that, under HMR, market share variance is lower and see less extreme market shares.]

[Discuss that, under SM, market share variance is very low and market shares are around 50/50].

>>>>

\begin{table}[ht]
\centering
\caption{Simultaneous Entry Needle In Haystack} 
\begin{tabular}{rlll}
  \hline
 & k = 20 & k = 100 & k = 200 \\ 
  \hline
TS vs DG & \makecell{\textbf{0.86} $\pm$0.02\\ eeog \\ avg: 14\\ med: 0} & \makecell{\textbf{0.65} $\pm$0.02\\ eeog \\ avg: 11\\ med: 0} & \makecell{\textbf{0.59} $\pm$0.02\\ eeog \\ avg: 6\\ med: 0} \\ 
  TS vs DEG & \makecell{\textbf{0.84} $\pm$0.02\\ eeog \\ avg: 20\\ med: 0} & \makecell{\textbf{0.62} $\pm$0.02\\ eeog \\ avg: 8\\ med: 0} & \makecell{\textbf{0.51} $\pm$0.03\\ eeog \\ avg: 5.4\\ med: 0} \\ 
  DG vs DEG & \makecell{\textbf{0.41} $\pm$0.02\\ eeog \\ avg: 400\\ med: 115} & \makecell{\textbf{0.47} $\pm$0.02\\ eeog \\ avg: 320\\ med: 0} & \makecell{\textbf{0.5} $\pm$0.02\\ eeog \\ avg: 290\\ med: 0} \\ 
   \hline
   \label{hm_nih}
\end{tabular}
\caption*{\tiny{The first line in each cell contains the average market share received by the firm playing Alg 1 (and the market share of Alg 2 is 1 - Alg 1 Market Share) as well as a 95 \% confidence band. For example, the cell in the top left indicates that TS gets on average 32\% of the market when played against DG. The next line contain the average and median effective end of game for this set of simulations.}}
\end{table}

\begin{table}[ht]
\centering
\caption{Simultaneous Entry Heavy Tail} 
\begin{tabular}{rlll}
  \hline
 & k = 20 & k = 100 & k = 200 \\ 
  \hline
TS vs DG & \makecell{\textbf{0.22} $\pm$0.02\\ eeog \\ avg: 0.27\\ med: 0} & \makecell{\textbf{0.41} $\pm$0.02\\ eeog \\ avg: 0.039\\ med: 0} & \makecell{\textbf{0.58} $\pm$0.02\\ eeog \\ avg: 12\\ med: 0} \\ 
  TS vs DEG & \makecell{\textbf{0.24} $\pm$0.02\\ eeog \\ avg: 3.2\\ med: 0} & \makecell{\textbf{0.48} $\pm$0.02\\ eeog \\ avg: 39\\ med: 0} & \makecell{\textbf{0.91} $\pm$0.01\\ eeog \\ avg: 84\\ med: 0} \\ 
  DG vs DEG & \makecell{\textbf{0.8} $\pm$0.02\\ eeog \\ avg: 16\\ med: 0} & \makecell{\textbf{0.86} $\pm$0.02\\ eeog \\ avg: 4.7\\ med: 0} & \makecell{\textbf{0.83} $\pm$0.02\\ eeog \\ avg: 2.7\\ med: 0} \\ 
   \hline
   \label{hm_ht}
\end{tabular}
\end{table}

@@

[IDEA: take a look at the distribution of reputation induced by each algorithm under each prior]

@@

Under the HardMax decision rule, firms need to incentivize consumers to select them over their competition by having a higher reputation. First, we consider the $HardMaxWithRandom$ decision rule discussed in the Section \ref{S:3}. Similar to the result in \citet{mansour2017competing} we find that this induces firms to play the ``better" algorithm for sufficiently long time horizon (see appendix). The intuition for this is the same as before, where, even though the firm initially suffers reputation loss from exploration, eventually the firm gets sufficiently many agents that don't need to be incentivized to select the firm in order to get a higher reputation than a ``worse" algorithm. We have a similar observation for the $SoftMax$ decision rule discussed in Section \ref{S:3}.

\begin{figure}
\label{agent_variances}
\end{figure}

We see that better algorithms are incentivized when we consider random agent response rules, but there are differences in the overall market composition. As Figure \ref{agent_variances} shows, the variance of market shares across simulations varies greatly. Under $HardMax$, we see that, in a single simulation, the market is generally ``winner take all" where one firm generally gets a large share of the market and there is a high variance. Under $HardMaxWithRandom$ we see that, in a single simulation, the market is mostly taken by one firm (but to a lower extent than under $HardMax$) and there is a lower, though still high, variance. Under $SoftMax$ we see that the market variance is very low and market shares are generally close to 50/50.
